\huge Open, privacy-preserving protocols for lawful surveillance

### 2016-02-27 paper/chaining.tex
Adding no-crypto text and updated graphs.

%These results are important in evaluating how practical our lawful contact-chaining protocol would be it were put into practice by government agencies and telecoms. However, our data set is relatively small compared to the databases held by real telecommunications companies, and each company handles that data using different technologies. The absolute running time and CPU usage of executing this protocol could vary from telecom to telecom. Therefore, we also produced a implementation of the contact-chaining protocol which omits all cryptographic operations. This version of the protocol does not preserve the privacy of users. By comparing the performance of our lawful contact-chaining protocol with the zero-privacy contact-chaining protocol, however, we can get a sense of the ``cost'' of privacy and accountability as compared to the practice of releasing plaintext data to government surveillance.

@@

\begin{figure*}[t]

\centering

\begin{subfigure}{.33\textwidth}

\centering

\includegraphics[width=0.99\textwidth]{runtime.pdf}

\captionsetup{justification=centering}

\caption{Protocol Runtime}

\label{fig:runtime}

\end{subfigure}\hfill

\begin{subfigure}{.33\textwidth}

\centering

\includegraphics[width=0.99\textwidth]{cputime.pdf}

\captionsetup{justification=centering}

\caption{CPU Time}

\label{fig:cputime}

\end{subfigure}\hfill

\begin{subfigure}{.33\textwidth}

\centering

\includegraphics[width=0.99\textwidth]{bandwidth.pdf}

\captionsetup{justification=centering}

\caption{Network Data}

\label{fig:data}

\end{subfigure}

\caption{Performance of Lawful Contact-Chaining}

\label{fig:performance}

\end{figure*}

@@

>>>>

These results are important in evaluating how practical our lawful contact-chaining protocol would be it were put into practice by government agencies and telecoms. However, our data set is relatively small compared to the databases held by real telecommunications companies, and each company handles that data using different technologies. The absolute running time and CPU usage of executing this protocol could vary from telecom to telecom. Therefore, we also produced a implementation of the contact-chaining protocol which omits all cryptographic operations. This version of the protocol does not preserve the privacy of users. By comparing the performance of our lawful contact-chaining protocol with the zero-cryptography contact-chaining protocol, however, we can get a sense of the ``cost'' of privacy and accountability as compared to the practice of releasing plaintext data to government surveillance.

@@

%Adding additional line breaks to this section will interfere with the formatting.
\begin{figure*}[t]
\centering
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.99\textwidth]{runtime.pdf}
\captionsetup{justification=centering}
\caption{Protocol Runtime}
\label{fig:runtime}
\end{subfigure}\hfill
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.99\textwidth]{cputime.pdf}
\captionsetup{justification=centering}
\caption{CPU Time}
\label{fig:cputime}
\end{subfigure}\hfill
\begin{subfigure}{.33\textwidth}
\centering
\includegraphics[width=0.99\textwidth]{bandwidth.pdf}
\captionsetup{justification=centering}
\caption{Network Data}
\label{fig:data}
\end{subfigure}
\caption{Performance of Lawful Contact-Chaining}
\label{fig:performance}
\end{figure*}

@@

The zero-cryptography version of our program ran, predictably, more quickly than the lawful privacy-preserving version. The total CPU time across all telecoms needed for our zero-crypto implementation never rose above ten seconds, even in the largest cases. This result allows us to disambiguate the cost of \emph{information retrieval} from \emph{privacy protection}. The linear relationship between the size of the encrypted user data set and the performance in terms of running time, CPU time, and network data usage of the protocol all remain even when we subrtract out the time to run all non-cryptgraphic parts of the protocol. We therefore conclude that, even given the potental database operations real telecoms would have to contend with, the cost of adding privacy-preservation to the contact-chaining protocol will remain reasonable.
